\section*{Use of Artificial Intelligence in Research Process}
\label{appendix:use_of_ai}

This appendix documents AI tool usage in accordance with Drexel University's academic integrity policies.

\subsection*{AI Tools and Applications}

\textbf{ChatGPT (GPT-4–5.1)} and \textbf{Claude (Claude 3–4.5 Sonnet)}: Sentence refinement, vocabulary suggestions, readability improvements, and formatting suggestions for written content. Code completion and scripting based on pseudocode for programming tasks (for "traditional" coding languages, visual patching and programming tasks were done by the researcher).

\textbf{GitHub Copilot}: Code completion (VS Code), syntax assistance, and commit message generation (GitHub Desktop). All core algorithms and cultural sonic encoding logic were independently designed.

\textbf{ComfyUI}: Visual ideation from original sketches (Sketch-to-Image) during conceptual development. \textit{No AI-generated images appear in this dissertation}.

\subsection*{Scope of Use}

AI tools were limited to:
\begin{itemize}[noitemsep]
	\item Language refinement (clarity, grammar, academic tone)
	\item Code efficiency for routine programming tasks
	\item Informal visual exploration (not included in final work)
\end{itemize}

All theoretical frameworks, research questions, analysis, interpretation, and conclusions are original work by the researcher.

\subsection*{Critical Approach}

Given this dissertation's focus on decolonial practice and cultural autonomy, AI tools were employed only as assistive technologies under human direction, without replacing cultural knowledge or lived experience. The researcher acknowledges ethical complexities including training data provenance, environmental impact, and potential biases.

\subsection*{Verification}

All AI-generated suggestions were critically evaluated, often substantially modified, and remain the researcher's sole responsibility. This disclosure was approved by the dissertation advisor.

\vspace{1.5em}

\emph{All content included in this document was reviewed, edited, and approved by the author. The use of AI tools complies with Drexel University’s academic integrity policies and was disclosed to and approved by the thesis advisor.}