
The following hardware components were utilized in the construction and operation of physical sculptures and sonic installations within this practice-based research.

\subsection*{Microcontrollers and Development Boards}

\begin{itemize}[topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=6pt]
	\item \textbf{Teensy 4.1}: \\ 
	PJRC. (2025). \textit{Teensy 4.1} [Microcontroller board].\\ 
	600 MHz ARM Cortex-M7, USB audio support, 8MB Flash, 1MB RAM.\\
	\url{https://www.pjrc.com/store/teensy41.html}
	
	\item \textbf{ESP32-S3 WROOM}: \\ 
	Freenove/Espressif Systems. (2025). \textit{ESP32-S3 WROOM Development Board} [Microcontroller with Wi-Fi/Bluetooth].\\ 
	Dual-core 32-bit processor, 240 MHz, wireless connectivity.\\
	\url{https://store.freenove.com/collections/for-esp32-s3}
	
	\item \textbf{Adafruit HUZZAH32 Feather ESP32 V2}: \\ 
	Adafruit Industries. (2025). \textit{Adafruit HUZZAH32 Feather ESP32 V2} [Microcontroller board].\\ 
	ESP32-based board with Wi-Fi/Bluetooth, Feather form factor.\\
	\url{https://www.adafruit.com/product/5400}
\end{itemize}

\subsection*{Sensors}

\begin{itemize}[topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=6pt]
	\item \textbf{Piezoelectric Disks}: \\ 
	Various manufacturers. (2025). \textit{Piezoelectric Disks} (27mm, 50mm) [Contact sensors].\\ 
	Brass/ceramic piezo elements for vibration and contact sensing.
	
	\item \textbf{GY-MAX4466 Electret Microphone}: \\ 
	Various manufacturers. (2025). \textit{GY-MAX4466 Electret Microphone Module} [Sound sensor].\\ 
	MAX4466 amplifier with adjustable gain (25x–125x), 20Hz–20kHz frequency response.\\
	Amplifier IC: Analog Devices MAX4466.\\
	\url{https://www.analog.com/en/products/max4466.html}
	
	\item \textbf{Adafruit MPR121 Capacitive Touch Sensor}: \\ 
	Adafruit Industries. (2025). \textit{MPR121 12-Key Capacitive Touch Sensor} [Touch sensor].\\ 
	12-channel capacitive touch sensing, I2C interface.\\
	\url{https://www.adafruit.com/product/1982}
	
	\item \textbf{Seeed Studio Grove GSR Sensor}: \\ 
	Seeed Studio. (2025). \textit{Grove Galvanic Skin Response (GSR) Sensor} [Physiological sensor].\\ 
	Measures electrical conductance of skin, Grove interface.\\
	\url{https://www.seeedstudio.com/Grove-GSR-sensor-p-1614.html}
\end{itemize}

\subsection*{Audio Hardware}

\begin{itemize}[topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=6pt]
	\item \textbf{Steinberg UR22C Audio Interface}: \\ 
	Steinberg Media Technologies. (2025). \textit{UR22C USB 3.0 Audio Interface} [Audio interface].\\ 
	32-bit/192kHz resolution, 2 inputs, 2 outputs, USB-C connectivity.\\
	\url{https://www.steinberg.net/audio-interfaces/ur22c/}
	
	\item \textbf{Zoom H5-Studio Handy Recorder}: \\ 
	Zoom Corporation. (2025). \textit{H5 Studio Handy Recorder} [Portable audio recorder].\\ 
	4-track simultaneous recording, 24-bit/96kHz, interchangeable microphone capsules.\\
	\url{https://zoomcorp.com/en/us/handheld-recorders/handheld-recorders/h5/}
	
	\item \textbf{Metal Marshmallow DIY-PH-29}: \\ 
	Metal Marshmallow. (2025). \textit{Marshmallow DIY Phantom (PH-29)} [Piezo preamplifier kit].\\ 
	Phantom-powered piezo disc preamp with adjustable gain.\\
	\url{https://metalmarshmallow.com/product.php?product_id=29}
\end{itemize}

\subsection*{MIDI and Control Devices}

\begin{itemize}[topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=6pt]
	\item \textbf{Akai MPK Mini}: \\ 
	Akai Professional. (2025). \textit{MPK Mini} [MIDI keyboard controller].\\ 
	25-key velocity-sensitive keyboard, 8 backlit pads, USB powered.\\
	\url{https://www.akaipro.com/mpk-mini-mk3}
	
	\item \textbf{AKG K371 Headphones}: \\ 
	AKG Acoustics/Harman. (2025). \textit{K371 Studio Headphones} [Monitor headphones].\\ 
	Closed-back, over-ear, 50mm drivers, 5Hz–40kHz frequency response.\\
	\url{https://www.akg.com/Headphones/Professional%20Headphones/K371.html}
\end{itemize}

\subsection*{Connectors and Cables}

\begin{itemize}[topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=6pt]
	\item \textbf{SparkFun Qwiic 4-Port Multiconnector}: \\ 
	SparkFun Electronics. (2025). \textit{Qwiic MultiPort} [I2C connector hub].\\ 
	4-port I2C distribution board for Qwiic/STEMMA QT systems.\\
	\url{https://www.sparkfun.com/products/18012}
	
	\item \textbf{2.54mm Pin Connectors}: \\ 
	Various manufacturers. (2025). \textit{2.54mm Pin Headers} (2-pin, 3-pin) [Electrical connectors].\\ 
	Standard 0.1" pitch pin headers for breadboard and PCB connections.
	
	\item \textbf{Amazon Basics 3.5mm Aux Cables}: \\ 
	Amazon Basics. (2025). \textit{3.5mm Audio Cable} (3m) [Audio cable].\\ 
	Male-to-male auxiliary audio cable.\\
	\url{https://www.amazon.com/AmazonBasics-3-5mm-Stereo-Audio-Cable/dp/B00NO73MUQ}
\end{itemize}

\subsection*{Tools and Materials}

\begin{itemize}[topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=6pt]
	\item \textbf{TS101 Soldering Iron}: \\ 
	Miniware. (2025). \textit{TS101 Smart Soldering Iron} with TS-B2 tip [Soldering tool].\\ 
	65W portable soldering iron, 50–400°C adjustable temperature, USB-C powered.\\
	\url{https://www.miniware.com.cn/product/ts101-soldering-iron/}
	
	\item \textbf{24 AWG Solid Core Copper Wire}: \\ 
	Tuofeng. (2025). \textit{24 AWG Solid Core Wire} [Hookup wire].\\ 
	Tinned copper conductor for electronics projects.
	
	\item \textbf{Copper Conductive Tape}: \\ 
	Various manufacturers. (2025). \textit{Copper Foil Tape} (2-inch width) [Conductive adhesive tape].\\ 
	Double-sided conductive adhesive for shielding and circuit connections.
\end{itemize}