% ============================================================
% A NOTE ON STRUCTURE
% ============================================================
% ~2 pages. Speaks plainly and academically to the institutional
% reader. Explains that the literature is threaded through the
% movements rather than collected in a prior chapter, and that
% this structural choice is methodologically consistent with
% research-creation: theory emerges from and in service of
% practice. Pre-empts committee concern about the absent
% dedicated literature review chapter.
% Key move: argue for the structure once, here, clearly —
% then the score is free to do what it needs to do.
% ============================================================

This dissertation does not follow what one would describe as a "conventional structure" of doctoral research. Not in the same sense as a more technically oriented field of study. There is no dedicated literature review chapter. There is no results section in the traditional sense. What follows, instead, is organized as a musical score: a Composer's Note, three Movements, and a Coda. This choice is just as much methodological as it is authentically stylistic. For work that arises primarily from personal practice entangled with fields such as Science and Technology Studies (STS) and Critical Making, it, perhaps, makes the most sense for it to take this form.  

The research proceeds from a \textit{research-creation} orientation, a practice-based approach to scholarly inquiry in which artistic making and critical thinking co-constitute one another \parencite{Loveless_2019}. In this framework, form and content are not separable. In fact, they can only be read as inseparable. The structure of the dissertation is itself an argument about how knowledge is produced and transmitted through embodied, culturally situated practice. It also inherits from the subtitle, "... as\textit{ Modification} for Embodied Practice." So, at the very least, consider it as such; a modification of standardized institutional form into something far more authentic to the study. To write about the making of three sonic sculptures inside a conventional IMRAD (Introduction, Methods, Results, and Discussion) structure would be to perform the very contradiction this work critiques: the imposition of a dominant epistemic form onto knowledge that arises from other, specific, agential cuts \parencites{Barad_2007}.

The three Movements of this dissertation correspond to three sculptural works: \textit{Buffalo Soldier} (Movement I: Substrate), \textit{Did Sun Ra Fear Cryosleep?} (Movement II: Water), and \textit{Don't Play with My Hair} (Movement III: Flesh). Each Movement proceeds through a series of named layers, logs, or sections that enact the methodological cycle of \textit{Speculocultural Technopoiesis} (ST): Unsettling, Remixing, Embodying, and Transmitting. These should not be read as case studies appended to a prior theoretical argument. They are the very conflict of the work itself. Theory \textit{emerging} from and in service of the making.

Theoretical literature does not appear in a prior chapter because, well, it is not prior. It arrives in each movement at the moment material demands it. Post-phenomenological accounts of mediation are summoned when the earth inside a wooden box begins to vibrate. Afrofuturist frameworks emerge when water holds a dissolving artifact in suspension. Scholarship on hair, touch, and bodily autonomy invades when a synthesis system tries and fails to read Black hair as data. In doing so, presenting an alternative relationship between theory and practice. One in which ideas are accountable to the materials that invoke them, rather than organized in advance of the work they are meant to illuminate.

The Composer's Note that precedes the Movements serves the function a conventional introduction would serve: it establishes the researcher's positionality, \textit{my} positionality. It articulates the central theoretical framework (\textit{Speculocultural Technopoiesis}), explains the organizing metaphor, and orients the reader to what follows. The Coda, which closes the dissertation, performs the work that a conventional conclusion and discussion would: it presents what was discovered, articulates contributions, and begins to open towards what remains to be done.

This Note makes the institutional argument for the form explicitly, so that the score itself is free to proceed without interruption.

So, thank you for attending, and please enjoy.
