\adnote{This chapter description from the proposal will function as the "roadmap" for the structure and contents of this dissertation chapter.}

%========================
% Epilogue — The Vessel Transformed (Proposal)
%========================

% \chapter*{Epilogue — The Vessel Transformed} % or \chapter if numbered in your class

This epilogue returns to the vessel after its voyage. The case studies named concrete patterns and operators; the discussion situated them within a broader theory of culturally specific mediation. What began as a critique of neutrality closes as a working practice for redesigning defaults. The vessel is no longer the same. It has \textit{transfigured} and \textit{metamorphosed}.

\begin{comment}
\subsubsection{Commitments to Transmission}
Transmission is not only distribution; it is care for how knowledge travels. The project commits to:
\begin{itemize}
	\item maintaining an open pattern library (operators, parameter schemas, minimal examples);
	\item coupling cultural rationales to code and UI affordances;
	\item supporting attribution choices (pseudonymity or named credit) for collaborators.
\end{itemize}

\subsubsection{Invitations and Open Questions}
\textbf{Adaptation.} How might the method translate—ethically and specifically—into other epistemic traditions?  
\textbf{Scale.} What happens when operators are embedded in mainstream toolchains and curricula?  
\textbf{Evaluation.} Which measures best capture entrainment, phrasing, and cultural authenticity at scale?
\end{comment}

\subsubsection{Objectives}
\begin{itemize}[noitemsep]
	\item Close the narrative arc by articulating how patterns/operators transform defaults.
	\item State concrete commitments for transmitting methods, code, and rationale.
	\item Pose focused invitations and questions that guide future research and adoption.
\end{itemize}

\begin{comment}
	% --- Epilogue Key References (keyword-based filter) ---
	\begin{refsection}[references.bib] % ensure items you want here have keyword=epilogue
		\nocite{*}
		\printbibliography[keyword=epilogue,heading=subbibliography,title={Key References}]
	\end{refsection}
\end{comment}
