% ============================================================
% COMPOSER'S NOTE — Opening
% ============================================================
% Brief orienting passage before the first named section.
% Sets the register: this is not a conventional academic
% introduction. Establishes that the reader is entering
% a score. Tone: deliberate, unhurried, present.
% ============================================================

What follows is a score for three instruments that do not yet fully exist.

Each instrument is a sonic sculpture built from earth, water, and hair---materials that carry memory, that have been contested and commodified, that vibrate differently depending on whose hands are present. The score documents the making of these instruments: the conceptual genesis, the technical decisions, the moments of friction where the tools pushed back, and the moments where something unexpected became possible. It also documents the framework that guided the making, \textit{Speculocultural Technopoiesis}, a method for converting speculative cultural imagination into material and sonic form.

A Composer's Note in a musical score typically addresses the performers. It explains what the composer was thinking, what the notation means, how the piece is meant to be approached. This note does the same. It addresses you---the reader, the committee, the future practitioner---and asks for a particular quality of attention: not the scanning eye of the evaluator, but the listening posture of someone who has agreed to follow sound into unfamiliar territory.

\adnote{This is a working draft opening. Adjust the tone and length once the full Composer's Note sections are drafted and you can feel the opening in relation to them.}
