% ============================================================
% COMPOSER'S NOTE § 1 — The Drone
% ============================================================
% Opens IN sound — not in argument, not in context-setting.
% Introduces sonic virtuality (Grimshaw & Garner) as the
% condition of possibility: sound as a field of potential
% that exists before any instrument conditions it.
% Sound is always already here — before the piezo is embedded,
% before the hydrophone is submerged, before the algorithm
% tries and fails to see hair.
% This is the drone: the perceptual constant that will hum
% through all three movements. Establishes the reader's ears
% before anything else.
%
% Key texts: Grimshaw & Garner — Sonic Virtuality
% ============================================================

\section*{The Drone}

It arrives through instruments, architectures, and digital systems that translate vibration into legible form. Forms with a specific history, a specific function, embedded and inherent. Sound is never neutral. Following Grimshaw and Garner's idea of \textit{sonic virtuality}, I consider sound as a field of potential that comes into being through the conditions of its mediation \parencite{Grimshaw_Garner_2015}. Each microphone, algorithm, or interface performs a conversion of energy, turning sonic potentials into technical expressions. This conversion---a kind of \textit{transduction}---is always shaped by the histories and values embedded in tools themselves.

This is the drone: the hum that was always already present, before any instrument shaped it into something hearable. Before the piezoelectric sensor was pressed into soil. Before the hydrophone was lowered into water. Before the computer vision system tried and failed to see Black hair as data. The drone does not begin when the work begins. It was already sounding. The three Movements of this dissertation are attempts to listen to it---to surface what has always been there, conditioning what was possible to hear.

\adnote{This section is extracted and re-voiced from \texttt{intro\_context.tex}. Consider expanding with a direct sonic image or a moment from the studio---something that opens \textit{in} sound before the theoretical framing of The Trombone section arrives.}
