% ============================================================
% COMPOSER'S NOTE § 2 — Who Is Making This
% ============================================================
% Positionality: Black scholar-practitioner, specific cultural
% grounding. Why specificity is generative rather than limiting —
% the specific-to-universal move: begin in one place deeply
% enough and you find principles that travel.
% Brief orientation to the three instruments and what they are —
% just enough to have a map, not a full description.
%
% Key texts:
%   Wynter — "The Ceremony Found": the autopoetic act of
%   re-envisioning the human; this dissertation as a sonic
%   ceremony finding.
% ============================================================

\section*{Who Is Making This}

As a Black/African-American male scholar-practitioner, I must acknowledge that the framework this research presents---and much of the research itself---emerges from my specific positionality and cultural background. The development of \textit{Speculocultural Technopoiesis} (ST) is deeply informed by Black epistemologies, cultural traditions, and theoretical perspectives that have shaped my own understanding of technology and creative practice. Rather than presenting this as a limitation, I position this specific cultural grounding as a strength that offers particular insights for addressing the shortcomings of many existing frameworks.

While the core structure of ST may be adaptable across different cultural contexts, my development and application of it is necessarily rooted in Black traditions and perspectives on sound and materiality. It is, specifically, a \textbf{Black} \textit{Sonic} Speculocultural Technopoiesis. This approach resonates with Sylvia Wynter's later articulation of ``The Ceremony Found,'' which names the autopoetic act of re-envisioning the human beyond Western epistemic closure \parencite{Wynter_2015}. In this sense, ST engages in a kind of sonic ceremony finding---a performative method that reveals the cultural specificity of universalized logics while opening space for alternative, speculative, and relational epistemologies.

I approach this research as both practitioner and scholar: an experimental media artist, designer, and musician whose creative practice informs a critical understanding of technology. Years of performance have taught me that precision---especially sonic precision---is always contextual to the craft, shaped by the body and the environment. This embodied sensibility extends into the digital: each algorithm, interface, or system becomes an instrument that can be re-tuned through creative modification. In this sense, my practice turns technological design into a form of musicianship, where making, listening, and reworking are inseparable.

My academic training spans dual Bachelor's degrees in Media Arts and Art Studio and a Master of Art and Design in Experimental Media Arts focused on sonic interaction and listening as interaction. Graduate minors in Digital Humanities and Computer Science have provided interdisciplinary grounding in systems thinking and interface development. Technically, my expertise includes real-time engines (Unity and Unreal), node-based procedural tools (Houdini, Max/MSP, TouchDesigner), and programming for interactive audio-visual systems---the very tools ST seeks to unsettle and reimagine through cultural intervention.

Across my practice, research, and teaching, I work to connect embodied Black sonic epistemologies with computational logic. Presentations at Ars Electronica (2023), the Atlantica Symposium on African Regroundings (2024), and the Media, Arts, and Design Conference (2024) reflect an ongoing commitment to research-creation as a mode of inquiry. This dual positioning as both artist and researcher enables me to integrate autoethnographic cultural knowledge with systematic technical rigor---capacities that ground the development of ST as both a theoretical framework and a practical methodology.

\adnote{Extracted from \texttt{intro\_researcher.tex} with light condensing. The qualifications paragraph can be trimmed further depending on how much institutional credentialing feels right in this register. The Wynter ``Ceremony Found'' citation needs to be confirmed in the .bib.}
