%\section{PREFATORY NOTE TO COMMITTEE}

This proposal comes to you while the Institutional Review Board (IRB) review process remains ongoing. A revised protocol was resubmitted on December 2, 2025, following feedback from the Drexel University IRB. \textit{No research involving human participants will begin until approval or exemption is obtained.}

A few points of orientation that may be helpful:

\textbf{On Methodology:} This dissertation employs collaborative autoethnography and practice-based research-creation methodologies that position collaborators as co-researchers and creative partners rather than traditional "subjects of study." This may potentially complicate standard IRB frameworks designed for experimental or observational research paradigms. These methodological considerations have been communicated to the IRB and are discussed in detail in Chapter 7 and Appendix B.

\textbf{On Timeline:} The research design anticipates this contingency. Technical development, infrastructure building, and solo autoethnographic practice can proceed independently of collaborative sessions while awaiting IRB determination.

\textbf{On Ethics:} Regardless of the IRB's final determination, the research maintains rigorous ethical commitments (informed collaboration, voluntary participation, clear attribution and consent protocols, and cultural respect) detailed in Chapter 7.

I welcome any questions the committee may have regarding these matters.

 \vspace{1.0em}
—\textit{ Darren Woodland, Jr.}

 \vspace{0.25em}
January 2026