The following software applications, protocols, and development tools were utilized in this practice-based research, thus far. All software is listed with version information current to the research period.
\label{pre:software}

\subsection*{Audio and Music Production}

\begin{itemize}[nosep]
	\item \textbf{Max}: 
	Cycling '74. (2025). \textit{Max} (Version 9) [Computer software]. 
	\\ \url{https://cycling74.com/products/max}
	
	\item \textbf{PlugData}: 
	PlugData Team. (2025). \textit{PlugData} [Computer software]. \\ \url{https://plugdata.org} Source code: \\ \url{https://github.com/plugdata-team/plugdata}
	
	\item \textbf{REAPER}: 
	Cockos Incorporated. (2025). \textit{REAPER} [Computer software]. 
	\\ \url{https://www.reaper.fm}
	
	\item \textbf{Spitfire Audio}:  
	Spitfire Audio. (2025). \textit{Spitfire Audio VST instruments} [Computer software]. 
	\\ \url{https://www.spitfireaudio.com}
\end{itemize}

\subsection*{Visual Programming and Real-Time Systems}

\begin{itemize}[nosep]
	\item \textbf{Houdini}:  
	SideFX. (2025). \textit{Houdini} (Version 21) [Computer software]. 
	\\ \url{https://www.sidefx.com}
	
	\item \textbf{TouchDesigner}:  
	Derivative. (2025). \textit{TouchDesigner} [Computer software]. 
	\\ \url{https://derivative.ca}
	
	\item \textbf{Unity}:  
	Unity Technologies. (2025). \textit{Unity} (Version 2022/6) [Computer software]. 
	\\ \url{https://unity.com}
\end{itemize}

\subsection*{Programming Languages and Development Tools}

\begin{itemize}[nosep]
	\item \textbf{Git}:  
	Software Freedom Conservancy. (2025). \textit{Git} (with Git LFS) [Computer software]. 
	\\ \url{https://git-scm.com}
	
	\item \textbf{GitHub}:  
	GitHub, Inc. (2025). \textit{GitHub} [Web-based platform]. 
	\\ \url{https://github.com}
	
	\item \textbf{Node.js}:  
	OpenJS Foundation. (2025). \textit{Node.js} [Computer software]. 
	\\ \url{https://nodejs.org}
	
	\item \textbf{Python}:  
	Python Software Foundation. (2025). \textit{Python} (Version 3) [Computer software]. 
	\\ \url{https://www.python.org} 
	Source code: \\ \url{https://github.com/python/cpython}
	
	\item \textbf{Thonny}:  
	Annamaa, A. (2025). \textit{Thonny} [Computer software]. 
	\\ \url{https://thonny.org} 
	Source code: \\ \url{https://github.com/thonny/thonny}
	
	\item \textbf{Visual Studio Code}:  
	Microsoft Corporation. (2025). \textit{Visual Studio Code} [Computer software]. 
	\\ \url{https://code.visualstudio.com} 
	Source code: \\ \url{https://github.com/microsoft/vscode}
\end{itemize}

\subsection*{Communication Protocols}

\begin{itemize}[nosep]
	\item \textbf{MIDI Protocol}:  
	MIDI Manufacturers Association. (1983/2025). \textit{MIDI 1.0 specification} [Communication protocol]. 
	\\ \url{https://www.midi.org}
	
	\item \textbf{OSC (Open Sound Control)}:  
	Wright, M., \& Freed, A. (2025). \textit{Open Sound Control 1.0 specification} [Communication protocol]. 
	Center for New Music and Audio Technologies, UC Berkeley.
	\\ \url{https://ccrma.stanford.edu/groups/osc/index.html}
\end{itemize}

\subsection*{Documentation and Design Tools}

\begin{itemize}[nosep]
	\item \textbf{Concepts}:  
	TopHatch, Inc. (2025). \textit{Concepts} [Mobile application]. 
	\\ \url{https://concepts.app}
	
	\item \textbf{Obsidian}:  
	Obsidian. (2025). \textit{Obsidian} [Computer software]. 
	\\ \url{https://obsidian.md}
\end{itemize}